Portfolio prioritization of salmon conservation

### 2013-05-11 inst/examples/salmonport.tex
Update md and tex after makefile run

\emph{Other title ideas:}\\- Portfolio optimization reveals\ldots{}\\-
something more general with animals instead of just salmon?\\- Portfolio
theory reveals conservation strategies that\ldots{}\\- Intelligent
tinkering with ecological portfolios: patterns of environmental response
diversity drive salmon conservation priorities\\- Keeping every cog and
wheel\ldots{}\\- A yin for every yang\ldots{}

>>>>

\emph{Other title ideas:} - Portfolio optimization reveals\ldots{} -
something more general with animals instead of just salmon? - Portfolio
theory reveals conservation strategies that\ldots{} - Intelligent
tinkering with ecological portfolios: patterns of environmental response
diversity drive salmon conservation priorities - Keeping every cog and
wheel\ldots{} - A yin for every yang\ldots{}
